Get Data

### 2022-02-11 get_data.Rmd
updated from hack meeting

```{r}
library(dplyr)
library(purrr)
```

@@

Things we need to do to update:

  - We need to put together a list of dois to pull from crossref.

@@

orcid_search(given_name = 'erin',
             family_name = 'buchanan')

erin_example <- orcid_person("0000-0002-9689-4189")

@@

@@

Ideas from meeting:
- Career length: from first pub, from first degree
- Over time: are things becoming more varied
- Maybe we can use scholar if they don't have orcid
- Which journals are publishing this information
- Types of big team research (social, cognitive)
- Employment levels
- Education levels
- # Of works: separate to total, other/preprint, journal/book/traditional
- Limitations of this system

>>>>

```{r}
library(dplyr)
library(purrr)
library(bib2df)
```

@@

@@

# find the names
erins_ids <- orcid_search(given_name = 'erin',
                          family_name = 'buchanan')
# if more than one pull ids 
nrow(erins_ids)
for (i in erins_ids$orcid){
  temp <- works(i)
  # check if the works includes a specific paper 
  # return only ones with that paper 
}

# erin_example <- orcid_person("0000-0002-9689-4189")

@@

table(erin_df$type)

erin_df$title_title_value <- tolower(erin_df$title_title_value)
erin_df$title_title_value <- gsub("[[:punct:]]", "", erin_df$title_title_value)
nrow(erin_df)

# remove real duplicates
temp <- erin_df[!duplicated(erin_df[ , c("type", "title_title_value") ]), ]
nrow(temp)

# combine types
erin_df$our_type <- erin_df$type
erin_df$our_type <- gsub("other|data-set|preprint", "open_science_pubs", erin_df$our_type)

table(erin_df$our_type)

erin_ed <- orcid_educations("0000-0002-9689-4189") %>% 
  as_tibble() %>%
  janitor::clean_names()

orcid_employments("0000-0002-9689-4189")

@@

Person statistics: 
- Career length: from first pub, from first degree
  `publication_date_year_value` anything 
- Employment levels
- Education levels
- # Of works: separate to total, other/preprint/data-set, journal/book/traditional
- Limitations of this system

Journal statistics: 
- Which journals are publishing this information
  - make sure preprints we are using also have real journal merged in 
- Types of big team research (social, cognitive)
  - keywords 
- Over time: are things becoming more varied
  - are the publications more varied over time
